---
title: "map_and_tilde"
author: "Patrick R. Wright"
date: "10/14/2020"
output: 
  md_document:
    variant: markdown_phpextra
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Using the map function with tilde (~) notations

In part inspired by [this](https://towardsdatascience.com/functional-programming-in-r-with-purrr-469e597d0229).

```{r libs}
# %>%
library(magrittr)
# map
library(purrr)
```

Map will apply a given function on each element of the input. The dot (.) indicated the object passed through by the pipe. In this case first the complete iris dataset and then a list of three data frames. One for each species in the iris dataset.

```{r split}
# split iris into a list by the different species and get the means for Sepal.Length and Sepal.Width
iris %>%
  split(.$Species) %>%
  map(~ c(mean(.$Sepal.Length),
          mean(.$Sepal.Width)))
```

The **tilde (~)** statement in the **map** call is equivalent to the following individual function and can thus replace the overhead of predefining a function.

```{r function}
means_sepal_iris <- function(data) {
    return(c(mean(data$Sepal.Length),
             mean(data$Sepal.Width)))
}
```

```{r map}
iris %>%
  split(.$Species) %>%
  map(means_sepal_iris)
```

```{r map2}
iris %>%
  split(.$Species) %>%
  map(function(.) { return(c(mean(.$Sepal.Length),
                             mean(.$Sepal.Width)))}
     )
```

```{r checks}
# Some sanity checks
mean(iris$Sepal.Length[which(iris$Species == "setosa")]) == 5.006
mean(iris$Sepal.Length[which(iris$Species == "versicolor")]) == 5.936
mean(iris$Sepal.Width[which(iris$Species == "virginica")]) == 2.974
```

```{r sessionInfo}
sessionInfo()
```

